\sys: Automated Data-Parallel Shell Processing

### 2020-05-01 pldi/draft.tex

The goal of this subsection is to evaluate \sys on an existing set of
unix pipelines found in the wild. \todo{Motivate why unix50 is a nice
  set of pipelines.} We took the solutions for the unix50 from
\todo{Ref} and we executed them \emph{without any modification} with
\sys's parallelism set to \todo{20}. The input given to the pipelines
was the test input from unix50 multiplied \todo{10000} times. The
speedup of each pipeline separately is shown in
\Cref{fig:unix50-individual}. The average\todo{/median} speedup is
\todo{5.24}.

%% The current average speedup includes unimplemented and small input pipelines.

%% Bad result descriptions:
%%  2. Contains just a head -n 2, and then a cut.
%%  5. Very fast (small input). Sequential time is 0m0.103s (If we increase the input we will show speedup)
%%  18. TODO: Implement
%%  20. Four corners (not parallelizable). So performance is reasonable
%%      (atm it doesn't return the correct result for multiplied input though)
%%  21. Last capital character of each line. Their solution is not general (and it is not parallelizable).
%%      Also, the input is very small. Changing it to a more general one and
%%      increasing input size leads to speedup. TODO: Run with large input
%%  22. Exactly the same problem as the above.
%%  24. (Not sure: It seems that the computation is trivial)
%%  32. TODO: Implement

%% WARNING: Remember to fix `sed` and not have it be stateless in general.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/unix50_individual_speedups_20.pdf}}
  \caption{
    \textbf{Speedup achieved by \sys for all pipelines with parallelism 20.}
    \todo{Scale the 0-1 region of the yaxis as much as the 1-20.}}
  \vspace{-15pt}
  \label{fig:unix50-individual}
\end{figure}

All pipelines that perform poorly (\todo{enumerate them}) contain
non-parallelizable commands. An illustrative example is pipeline
\todo{X}, which is shown here:

\begin{lstlisting}[language=sh, float=h, numbers=none]
  TODO
\end{lstlisting}

Notice in the above the use of (awk, fmt, or something else). We
noticed that these occured in other pipelines too. By changing them to
\todo{X}, the average speedup of these pipelines improved to \todo{x}
and the new total average speedup is \todo{X}.

>>>>

The goal of this subsection is to evaluate \sys on an existing set of
unix pipelines found in the wild. \todo{Motivate why unix50 is a nice
  set of pipelines.} We took the solutions for the unix50 from
\todo{Ref} and we executed them \emph{without any modification} with
\sys's parallelism set to \todo{16}. The input given to the pipelines
was the test input from unix50 multiplied to reach \todo{10GBs}. The
speedup of each pipeline separately is shown in
\Cref{fig:unix50-individual}. The average\todo{/median} speedup is
\todo{5.24}.

%% Breakdown of not ideal speedups in 8, 16 parallelism

%% Head: 2, 19, 31
%% Sort-bottleneck: 1, 3, 15, 16, 20, 33
%% Non-parallelizable completely: 13 (awk-solved), 18 (awk), 24, 25, 26, 29, 30
%% Cheap (non cpu intensive -- constant costs grow): 0, 4, 5, 6, 7, 8, 12, 14
%% Long (task-based parallelism in sequential and context switches): 7, 8, 9, 10, 11, 12, 14, 21, 27, 28

\kk{Out of all benchmarks, we have talked about the head and the
  non-parallelizable ones in the paper. Maybe we also want to talk
  about the long and the cheap ones. Also we might want to talk and
  find out more about the sort bottleneck.}

%% (OLD) Bad result descriptions:
%%  2. Contains just a head -n 2, and then a cut.
%%  5. Very fast (small input). Sequential time is 0m0.103s (If we increase the input we will show speedup)
%%  18. TODO: Implement
%%  20. Four corners (not parallelizable). So performance is reasonable
%%      (atm it doesn't return the correct result for multiplied input though)
%%  21. Last capital character of each line. Their solution is not general (and it is not parallelizable).
%%      Also, the input is very small. Changing it to a more general one and
%%      increasing input size leads to speedup. TODO: Run with large input
%%  22. Exactly the same problem as the above.
%%  24. (Not sure: It seems that the computation is trivial)
%%  32. TODO: Implement

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/unix50_individual_speedups_16.pdf}}
  \caption{ \textbf{Speedup achieved by \sys for all pipelines with
      parallelism 16. The red bars are the sequential execution time
      of each pipeline.}
    %% \todo{Scale the 0-1 region of the yaxis as much as the 1-20.}
  }
  \vspace{-15pt}
  \label{fig:unix50-individual}
\end{figure}

\TODO{An important point that needs to be made clear is that these are
  taken from the wild unmodified. And that Pash never leads to
  slowdown (except for the trivial head cases, where the slowdown is
  neligible).}

\sys achieves speedup in all pipelines except for 2, 19, and 31. These
pipelines include a \ttt{head} and only process one line of the
input. This can be seen by their sequential execution time which is in
the order of 10 milliseconds. The slowdown is due to constant costs of
setting up the pipes and spawning many processes. In all three of
these cases the execution time with \sys is in the order of \todo{X
  ms}. For pipelines 13, 24, 25, 26, 29, and 30, \sys performs the
same as the sequential implementation. This is because these pipelines
contain non-parallelizable commands, such as \ttt{awk}, \ttt{sed} with
option \ttt{d}, and \ttt{tr} with option \ttt{-d}. An illustrative
example is pipeline 13, which is shown here:

\begin{lstlisting}[language=sh, float=h, numbers=none]
  cat $IN | awk "{print \$2, \$0}" | sort -nr | cut -d ' ' -f 2
\end{lstlisting}

\kk{Rephrase that to sound more meaningful and surprising.}  Notice
that \ttt{awk} is just used to permute two of the columns of the input
to enable sorting. One could write this pipeline in a different way,
by directly sorting on the second column:

\begin{lstlisting}[language=sh, float=h, numbers=none]
  cat $IN6 | sort -nr -k 2 | cut -d ' ' -f 1
\end{lstlisting}

By executing this version of the pipeline with \sys, we achieve
\todo{X} speedup. This indicates that just a little awaresess of
command parallelizability can go a long way, and that the effort that
a \sys user needs to spend is often negligible to achieve
benefits. Finally, an important point that is reinforced from this
experiment is that \sys doesn't lead to slowdown, even in cases where
parallelism is not possible.
